\documentclass[10pt,letterpaper]{article} % Standard class, common font sizes

%--------------------------------------------------------------
% PACKAGES
%--------------------------------------------------------------
\usepackage[utf8]{inputenc} % Input encoding
\usepackage[T1]{fontenc}    % Font encoding
% \usepackage{lmodern}      % Using TeX Gyre Pagella instead
\usepackage{tgpagella}      % Palatino clone - stylish and professional
\usepackage[margin=0.75in]{geometry} % Margins
\usepackage{hyperref}       % Clickable links
\usepackage{needspace}      % Prevent awkward page breaks
\usepackage{enumitem}       % For custom list spacing if needed
\usepackage{sectsty}        % To style section headings
\usepackage{titlesec}       % More control over section titles
\usepackage{textcomp}       % For symbols like copyright, etc.
\usepackage{array}          % For the skills section table (simple one)
\usepackage{fontawesome5}   % For icons like GitHub, LinkedIn (optional, ensure it's installed)

%--------------------------------------------------------------
% STYLING & FORMATTING (ATS-FRIENDLY)
%--------------------------------------------------------------

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue, % Or black for print
    urlcolor=blue,  % Or black for print
    pdftitle={Intiser Ahmed - Resume},
    pdfauthor={Intiser Ahmed},
    pdfkeywords={Software Engineer, Mobile Developer, AI, iOS, Android, Flutter, Full Stack, Intiser Ahmed} % Add relevant keywords
}

% Remove page numbers (optional, common for resumes)
\pagestyle{empty}

% Section heading style
\titleformat{\section}{\Large\bfseries\raggedright}{}{0em}{}[\titlerule\vspace{0.5ex}]
\titlespacing*{\section}{0pt}{1.5ex}{1ex} % Adjust spacing around section titles

% Subsection heading style (for job titles, project names etc.)
\titleformat{\subsection}{\large\bfseries\raggedright}{}{0em}{}
\titlespacing*{\subsection}{0pt}{1ex}{0.5ex}

% Reduce spacing for itemize environments
\setlist[itemize]{nosep, leftmargin=*} % Remove vertical spacing in lists, adjust left margin

% Command for contact items
% Using FontAwesome icons for a more stylish look, with text fallback for ATS
\newcommand{\contactItem}[2]{\noindent\textbf{#1: }\href{#2}{\texttt{#2}}}
\newcommand{\contactItemPlain}[2]{\noindent\textbf{#1: }\texttt{#2}}
\newcommand{\contactLinkFA}[4]{\noindent\faIcon{#1} \href{#2}{\texttt{#3}} (#4) } % Icon, Link, Text, PlainTextForATS
\newcommand{\contactLink}[3]{\noindent\textbf{#1: }\href{#2}{\texttt{#3}}}


% Command for job details (dates, location)
\newcommand{\jobDetailsLine}[1]{\noindent\textit{#1}\par\vspace{0.5ex}}

% Command for skill categories
\newcommand{\skillCategory}[1]{\noindent\textbf{#1: }}

%--------------------------------------------------------------
% YOUR DEFINED COMMANDS (FROM ORIGINAL) - KEPT FOR CONTENT EXTRACTION
%--------------------------------------------------------------
\newcommand{\yourName}{Intiser Ahmed}
\newcommand{\yourWebsiteText}{Portfolio: intiser.space} % Changed for clarity
\newcommand{\yourWebsiteLink}{https://intiser.space}
\newcommand{\yourEmail}{intiser4@gmail.com}
\newcommand{\yourPhone}{+60-1126149106}
\newcommand{\githubUserName}{intiserahmed}
\newcommand{\linkedInUserName}{intiser-ahmed}

%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%   PROFILE
%--------------------------------------------------------------
\begin{center}
    {\Huge\bfseries \yourName} \\ \vspace{3pt}
    \contactLink{\faGlobe}{https://intiser.space}{intiser.space} \textbullet{}
    \contactLink{\faEnvelope}{mailto:\yourEmail}{\yourEmail} \textbullet{}
    \contactItemPlain{\faMobileAlt}{\yourPhone} \\ \vspace{2pt}
    \contactLink{\faLinkedin}{https://www.linkedin.com/in/\linkedInUserName}{linkedin.com/in/\linkedInUserName} \textbullet{}
    \contactLink{\faGithub}{https://github.com/\githubUserName}{github.com/\githubUserName}
\end{center}
\vspace{1ex}

%--------------------------------------------------------------
%   SUMMARY / PROFESSIONAL PROFILE (Optional, but good for a quick pitch)
%--------------------------------------------------------------
\section*{Professional Profile}
Senior Mobile Engineer \& AI Innovator with 4+ years of experience delivering impactful results across 4 countries (USA, Singapore, Malaysia, Bangladesh) – both remote and onsite. Specializing in iOS (SwiftUI/UIKit), Flutter, and applied AI to solve real-world challenges in accessibility, healthcare, and industrial automation. Apple WWDC Swift Student Challenge Winner (2021). Proven ability to lead teams, drive community growth (1200\%+), and develop solutions saving millions annually through automation.

%--------------------------------------------------------------
%   RESEARCH INTERESTS
%--------------------------------------------------------------
% \section*{Research Interests} % Combined into Professional Profile for brevity or can be separate
% AI for healthcare, accessibility, and industrial automation. Interested in multimodal learning, few-shot medical imaging, privacy-preserving LLMs, and NLP for assistive technology.

%--------------------------------------------------------------
%   EDUCATION
%--------------------------------------------------------------
\section{Education}
\subsection*{International Islamic University Malaysia} % Institution as subsection
\noindent\textbf{BSc. Honours Computer Science With Software Engineering Specialization} \\
\jobDetailsLine{Kuala Lumpur, MY \textbullet{} Mar 2024}
\textbf{CGPA: 3.52}

%--------------------------------------------------------------
%   SKILLS
%--------------------------------------------------------------
\section{Skills}
\skillCategory{Mobile Development} iOS (Swift, SwiftUI, UIKit, Objective-C, Combine, RxSwift, CoreML, CreateML), Android (Kotlin, Jetpack Compose), Flutter (Dart, BLoC, Riverpod, GetX, Flavors). \\ \vspace{0.5ex}
\skillCategory{Frontend Web} ReactJS, NextJS, JavaScript, TypeScript, HTML, CSS, Tailwind CSS, Framer Motion. \\ \vspace{0.5ex}
\skillCategory{Backend} Node.js, Python (Django, FastAPI), Dart (Server-side). \\ \vspace{0.5ex}
\skillCategory{AI/ML} TensorFlow, PyTorch, Keras, Hugging Face, ONNX, Core ML, On-Device AI (Whisper, Phi-3, Llama-3), Model Quantization, Fine-Tuning. \\ \vspace{0.5ex}
\skillCategory{Databases} MongoDB, MySQL, PostgreSQL, Firebase, Supabase, Azure SQL DB, SQLite, Hive. \\ \vspace{0.5ex}
\skillCategory{Cloud | CI/CD | Tools} AWS (Solutions Architect Certified), Docker, Jenkins, Github Actions, Fastlane, Xcode Cloud, TestFlight, App Center, Google Play Console, Jira, Git, Netlify, Vercel, Heroku.

%--------------------------------------------------------------
%   APP SHOWCASE
%--------------------------------------------------------------
\section{App Showcase}

\subsection*{Gazey Talk (iOS, Android - Beta)}
\noindent Founder & Lead Developer of an innovative assistive eye-tracking communication app, empowering users with speech difficulties. Features advanced AI for gaze detection and predictive text. \\
\textit{Core Tech: SwiftUI, Jetpack Compose, Kotlin, Swift, On-Device AI. \textbullet{} \href{https://gazeytalk.com/}{gazeytalk.com}}
\vspace{0.5ex}

\subsection*{AI Medical Transcription (iOS/macOS - Beta)}
\noindent Secure, on-device AI medical transcription app ensuring patient data privacy by processing audio entirely locally. Designed for healthcare professionals to streamline documentation. \\
\textit{Core Tech: Swift, SwiftUI, CoreML, On-Device Whisper models.}
\vspace{0.5ex}

\subsection*{Continental AG - R&D Automation App (Flutter)}
\noindent Delivered an AI-powered app for tire sidewall recognition and warehouse process automation across 12+ countries, achieving 85\% time savings and millions in annual savings. \\
\textit{Core Tech: Flutter, AI (Image Recognition), MS SQL, API Integration.}
\vspace{0.5ex}

\subsection*{Smart Walkie - VoicePing (iOS)}
\noindent Key contributor to a real-time PTT communication app. Overhauled legacy code, implemented Opus codec for optimal audio, and significantly improved app performance (30\% battery, 20\% crash reduction). \\
\textit{Core Tech: Swift, Objective-C, SwiftUI, UIKit, Combine, WebRTC. \textbullet{} \href{https://apps.apple.com/my/app/voiceping/id1249953303}{App Store}}
\vspace{1ex}

%--------------------------------------------------------------
%   EXPERIENCE
%--------------------------------------------------------------
\section{Experience}

\subsection*{Smart Walkie Pte. Ltd.}
\noindent\textbf{Senior iOS Engineer} \\
\jobDetailsLine{Singapore (Contract) \textbullet{} May 2024 – Dec 2025 (Expected)}
% \textit{Links: \href{https://www.smartwalkie.com}{www.smartwalkie.com} \textbullet{} \href{https://apps.apple.com/my/app/voiceping/id1249953303}{VoicePing App Store}} % Link in Showcase
\begin{itemize}
    \item Overhauled legacy code infrastructure, transitioning to contemporary libraries and frameworks (SwiftUI, Combine), ensuring long-term stability and support.
    \item Implemented optimal audio processing using Opus codec and integrated voice processing for real-time communication, enhancing audio quality and efficiency.
    \item Optimized app performance: Reduced battery consumption by 30\% and crash rate by 20\% through targeted optimizations using Xcode Instruments and Network Conditioner.
\end{itemize}
\textit{Technologies used: Swift, Objective-C, SwiftUI, UIKit, Combine, WebRTC, Opus Codec, Xcode Instruments, TestFlight, Network Conditioner.}
\vspace{1ex}

\subsection*{Gazey Talk}
\noindent\textbf{Founder \& Lead Mobile App Developer} \\
\jobDetailsLine{Petaling Jaya, MY \textbullet{} Mar 2024 – Present}
% \textit{Link: \href{https://gazeytalk.com/}{www.gazeytalk.com}} % Link in Showcase
\begin{itemize}
    \item Led the full-cycle development of Gazey Talk, an innovative advanced assistive eye tracking app for communication across iOS (SwiftUI) and Android (Jetpack Compose, Kotlin), currently in beta.
    \item Architected and implemented on-device AI algorithms for gaze detection and predictive text input, enhancing user experience and accessibility.
    \item Led a team of developers, ensuring adherence to project timelines, optimizing task allocation, and maintaining high code quality standards through agile methodologies.
    \item Collaborated extensively with stakeholders, therapists, and potential users to gather comprehensive requirements, define innovative features, and strategically prioritize the product roadmap.
\end{itemize}
\textit{Technologies used: SwiftUI, Swift, UIKit, Jetpack Compose, Kotlin, On-Device AI, Next.js (Landing Page), React.js, Fastlane, Jira, App Center, TestFlight.}
\vspace{1ex}

\subsection*{Continental AG}
\noindent\textbf{Mobile Application Developer Intern} \\
\jobDetailsLine{Petaling Jaya, MY \textbullet{} Aug 2023 – Feb 2024}
% \textit{Link: \href{https://www.continental-tires.com/my/en/}{www.continental-tires.com}} % Implied by Showcase
\begin{itemize}
    \item \textbf{Designed, Developed, and Delivered} an R\&D app (Flutter) featuring AI Tire Side Wall Recognition, QR/Barcode scanning, and API integration. \textbf{Automated} warehouse processes across \textbf{12+ countries}, resulting in \textbf{85\%} time savings, \textbf{99\%} human error reduction, and \textbf{millions} saved annually.
    \item \textbf{Initiated and Developed} an Event App Registrar (Flutter) automating attendee registration with QR codes and NFC tags, registering \textbf{18,000+ attendees} across international events.
    \item Optimized commercial Flutter SDK with refined code for robust exception handling and bug fixing, achieving a \textbf{30\% reduction} in reported issues.
\end{itemize}
\textit{Technologies used: Flutter, BLoC, Dart, Swift (Native Modules), AI (Image Recognition), REST API, SDK Integration, MS SQL, Jenkins, Jira, Appium, App Center, UAT.}
\vspace{1ex}

\subsection*{Computational Intelligence Research Group, IIUM}
\noindent\textbf{Trainer} \\
\jobDetailsLine{Kuala Lumpur, MY \textbullet{} June 2022 – Aug 2023}
\textit{Link: \href{https://linktr.ee/ciirgiium}{linktr.ee/ciirgiium}}
\begin{itemize}
    \item Trained and mentored over 100 students on practical applications of AI (Computer Vision, NLP) and IoT technologies using Python, TensorFlow, and Raspberry Pi.
    \item Inspired student-led innovations including a hand glove-based sign language recognition system and a smart mirror powered by AI.
    \item Encouraged interdisciplinary thinking and ethical development aligned with real-world accessibility and automation challenges.
\end{itemize}
\vspace{1ex}

\subsection*{ATSIGN}
\noindent\textbf{Full-Stack Mobile Application Developer} \\
\jobDetailsLine{San Jose, USA (Remote) \textbullet{} Aug 2021 – Sep 2022}
\textit{Link: \href{https://www.atsign.com}{www.atsign.com}}
\begin{itemize}
    \item Architected and deployed a robust Dart server-side API using Docker, optimizing data security and reducing latency by 35\%, thereby elevating system performance for peer-to-peer applications.
    \item Revolutionized \textit{SpaceChat} (Flutter) application by developing advanced messaging and group features & implementing automated testing (integration, unit), cutting development time by 60\% and accelerating product release cycles.
    \item Engineered a MicroPython SDK for Atsign, integrating with Raspberry Pi devices to enhance IoT connectivity and streamline secure device management.
\end{itemize}
\textit{Technologies used: Flutter, Dart, Swift (Native Modules), Kotlin (Native Modules), Docker, MicroPython, Raspberry Pi, C++, Jenkins, App Store Connect, Google Play Console, Test-Driven Development.}
\vspace{1ex}

\subsection*{ATSIGN}
\noindent\textbf{Full-Stack Developer Intern} \\
\jobDetailsLine{San Jose, USA (Remote) \textbullet{} May 2021 – July 2021}
\begin{itemize}
    \item Developed official developer site using React and Next.js, following Agile sprint cycles to enhance user experience and increase developer engagement by 75\%.
    \item Collaborated in the development and execution of comprehensive testing protocols for a secure Full-stack Flutter App, integrating Atsign SDK.
\end{itemize}
\textit{Technologies used: Flutter, Kotlin, JavaScript, ReactJS, SCSS, Tailwind CSS, NextJS, Github Actions.}
\vspace{1ex}

\subsection*{ATSIGN}
\noindent\textbf{Technical Support Engineer} \\
\jobDetailsLine{San Jose, USA (Remote) \textbullet{} Dec 2020 – April 2021}
\begin{itemize}
    \item Spearheaded the development and demonstration of full-stack Demo Apps (Flutter), facilitating experiential learning for developers and propelling the successful deployment of multiple apps on the App Store.
    \item Elevated developer engagement by 30\% through comprehensive documentation, tutorials, and insightful articles on Atsign SDK architecture, catalyzing community growth.
    \item Optimized 8 global live events and hackathons, providing real-time technical troubleshooting and enhancing participant engagement.
\end{itemize}
\textit{Technologies used: Technical Writing, Documentation, Flutter, Atsign SDK, Docker, App Store Connect.}
\vspace{1ex}


%--------------------------------------------------------------
%   PERSONAL PROJECTS
%--------------------------------------------------------------
\section{Personal Projects}

\subsection*{ZapShorts (Ongoing)}
\noindent AI-powered video clipping tool to transform long-form videos into viral-ready short clips. Features AI Clipping, Animated Captions, B-Roll integration, Virality Score, platform-specific exports (TikTok, YouTube Shorts), social media scheduling, and brand template customization (logos, intros/outros). \\
\textit{Technologies: Python (Backend), AI (Video Analysis, NLP), Next.js (Frontend), Cloud Services.}
\vspace{0.5ex}

% AI Medical Transcription App & macOS File Organization App are now in App Showcase
% \subsection*{AI Medical Transcription App (iOS/macOS, TestFlight Beta)} ...
% \subsection*{macOS File Organization App (TestFlight Beta)} ...

\subsection*{Spectreora (2023)}
\noindent Portable, non-mobile reliant IoT ecosystem for continuous cardiac monitoring and real-time stroke prediction. \href{https://github.com/Intiserahmed/SpectreOra-IoT-Mobile-ML}{\faGithubSquare~GitHub Link} \\
\textit{Technologies: Micropython, C++, Flutter, Riverpod, AWS, Python, FastAPI, PostgreSQL, Supabase, Firebase.}
\vspace{0.5ex}

\subsection*{Sacred Fort (2021)}
\noindent Robust Password Manager App enabling secure storage, update, sharing, and autofill of passwords for websites and apps. \href{https://github.com/Intiserahmed/Password-Manager-Atsign}{\faGithubSquare~GitHub Link} \\
\textit{Technologies: Flutter, Kotlin (Autofill), Atsign SDK, Getx, Hive.}
\vspace{0.5ex}

\subsection*{Portfolio Site (intiserahmed.online)}
\noindent Personal portfolio website to showcase projects and skills. \href{https://intiserahmed.online/}{\faGlobe~Link} \\
\textit{Technologies: NextJS, ReactJS, TypeScript, Tailwind CSS, Vercel, Vite.}
\vspace{1ex}

\noindent\textbf{\textit{More Projects on \href{https://github.com/intiserahmed}{\faGithubSquare~GitHub: github.com/intiserahmed}}}

%--------------------------------------------------------------
%   RECOGNITION, AWARDS & CERTIFICATIONS
%--------------------------------------------------------------
\section{Recognition & Leadership}
\begin{itemize}
    \item \textbf{GDSC Lead, Google Developer Student Club IIUM (2021-2022):} Led and managed a team of 21 to organize events and hackathons, fostering innovation and community engagement. Grew club membership by 1233\%.
    \item \textbf{Mentor:} Stanford University's TreeHacks (2021); Princeton University's HackPrinceton (2021 - Mentor & Judge); UC Berkeley's CalHack (2021).
    \item \textbf{Streamlit Student Ambassador.}
\end{itemize}

\subsection*{Awards}
\begin{itemize}
    \item \textbf{Apple WWDC Swift Student Challenge Winner (2021)}
    \item IIUM Dean's Award (2020 - 2024)
    \item Silver, Final Year Project, IIUM (2023)
\end{itemize}

\subsection*{Certifications}
\begin{itemize}
    \item AWS Cloud Solutions Architect (2023)
    \item Deloitte Australia Technology Virtual Experience Program (2023)
    \item MongoDB for SQL Experts (2023)
    \item Postman API Student Expert (2023)
    \item Cisco CyberOps Associate (2021)
\end{itemize}

%--------------------------------------------------------------
%   REFERENCES
%--------------------------------------------------------------
\section*{References} % Unnumbered section
Available upon request. Testimonials viewable on LinkedIn: \href{https://www.linkedin.com/in/intiser-ahmed/details/recommendations/}{\faLinkedin~linkedin.com/in/\linkedInUserName/details/recommendations/}

\end{document}